Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-09 MDPI_submission.Rmd
Commit 2023-11-09 05:11

```{r cusummonth, echo = FALSE, fig.cap='Cumulative sum plots of the monthly SDR anomalies in (%) for different sky conditions.', fig.subcap=c('All skies.', 'Clear skies.', 'Cloudy skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeMonthlyCuSum-1.png",    # ALL sky
    "./images/CumulativeMonthlyCuSum-5.png",    # CLEAR sky
    "./images/CumulativeMonthlyCuSum-9.png"))   # Cloud sky
```

@@

```{r cusumnotrendmonthly, echo = FALSE, fig.cap='Cumulative sum plots of monthly SDR anomalies in (%) for different sky conditions after removing the long-term linear trend.', fig.subcap=c('All skies.', 'Clear skies.', 'Cloudy skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeMonthlyCuSumNOtrend-1.png",    # ALL sky
    "./images/CumulativeMonthlyCuSumNOtrend-5.png",    # CLEAR sky
    "./images/CumulativeMonthlyCuSumNOtrend-9.png"))   # Cloud sky
```

@@

>>>>

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
        \subfloat[All skies.\label{fig:cusummonth-1}]
            {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-1}}\hfill
        \subfloat[Clear skies.\label{fig:cusummonth-2}]
            {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-5}}\hfill
        \subfloat[Cloudy skies.\label{fig:cusummonth-3}]
            {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-9}}\hfill
        }
\caption{Cumulative sum plots of the monthly SDR anomalies in (\%) for different sky conditions.}\label{fig:cusummonth}
\end{adjustwidth}
\end{figure}

<!-- ```{r cusummonth, echo = FALSE, fig.cap='Cumulative sum plots of the monthly SDR anomalies in (%) for different sky conditions.', fig.subcap=c('All skies.', 'Clear skies.', 'Cloudy skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics(c( -->
<!--     "./images/CumulativeMonthlyCuSum-1.png",    # ALL sky -->
<!--     "./images/CumulativeMonthlyCuSum-5.png",    # CLEAR sky -->
<!--     "./images/CumulativeMonthlyCuSum-9.png"))   # Cloud sky -->
<!-- ``` -->

@@

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]
                {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-1} }\hfill
            \subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]
                {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-5} }\hfill
            \subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]
                {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-9} }
        }
\caption{Cumulative sum plots of monthly SDR anomalies in (\%) for different sky conditions after removing the long-term linear trend.}\label{fig:cusumnotrendmonthly}
\end{adjustwidth}
\end{figure}

<!-- ```{r cusumnotrendmonthly, echo = FALSE, fig.cap='Cumulative sum plots of monthly SDR anomalies in (%) for different sky conditions after removing the long-term linear trend.', fig.subcap=c('All skies.', 'Clear skies.', 'Cloudy skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics(c( -->
<!--     "./images/CumulativeMonthlyCuSumNOtrend-1.png",    # ALL sky -->
<!--     "./images/CumulativeMonthlyCuSumNOtrend-5.png",    # CLEAR sky -->
<!--     "./images/CumulativeMonthlyCuSumNOtrend-9.png"))   # Cloud sky -->
<!-- ``` -->

@@

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}

{\centering \subfloat[All skies.\label{fig:szatrends-1}]{\includegraphics[width=.32\linewidth]{./images/SzaTrends-1} }\subfloat[Clear skies.\label{fig:szatrends-2}]{\includegraphics[width=.32\linewidth]{./images/SzaTrends-4} }\subfloat[Cloudy skies.\label{fig:szatrends-3}]{\includegraphics[width=.32\linewidth]{./images/SzaTrends-7} }

}

\caption{Long term trends of SDR as a function of SZA separately form morning and afternoon periods. Solid shapes  represent statistically significant trends ($p < 0.005$).}\label{fig:szatrends}
\end{adjustwidth}
\end{figure}

### 2023-11-09 MDPI_submission.tex
Commit 2023-11-09 04:14
Commit 2023-11-09 05:11

\usepackage{subcaption}
\captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.17}, aboveskip=6pt,  belowskip=-6pt, singlelinecheck=off, justification=justified}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

{\centering \subfloat[All skies.\label{fig:cusummonth-1}]{\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-1} }\subfloat[Clear skies.\label{fig:cusummonth-2}]{\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-5} }\subfloat[Cloudy skies.\label{fig:cusummonth-3}]{\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-9} }

\caption{Cumulative sum plots of the monthly SDR anomalies in (\%) for different sky conditions.}\label{fig:cusummonth}
\end{figure}

@@

{\centering \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]{\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-1} }\subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]{\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-5} }\subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]{\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-9} }

\caption{Cumulative sum plots of monthly SDR anomalies in (\%) for different sky conditions after removing the long-term linear trend.}\label{fig:cusumnotrendmonthly}
\end{figure}

@@

>>>>

\usepackage{subcaption}
\captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.17}, aboveskip=6pt,  belowskip=-6pt, singlelinecheck=off, justification=justified}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
        \subfloat[All skies.\label{fig:cusummonth-1}]
            {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-1}}\hfill
        \subfloat[Clear skies.\label{fig:cusummonth-2}]
            {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-5}}\hfill
        \subfloat[Cloudy skies.\label{fig:cusummonth-3}]
            {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSum-9}}\hfill
        }
\caption{Cumulative sum plots of the monthly SDR anomalies in (\%) for different sky conditions.}\label{fig:cusummonth}
\end{adjustwidth}
\end{figure}

@@

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]
                {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-1} }\hfill
            \subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]
                {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-5} }\hfill
            \subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]
                {\includegraphics[width=.32\linewidth]{./images/CumulativeMonthlyCuSumNOtrend-9} }
        }
\caption{Cumulative sum plots of monthly SDR anomalies in (\%) for different sky conditions after removing the long-term linear trend.}\label{fig:cusumnotrendmonthly}
\end{adjustwidth}
\end{figure}

@@

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}

\caption{Long term trends of SDR as a function of SZA separately form morning and afternoon periods. Solid shapes  represent statistically significant trends ($p < 0.005$).}\label{fig:szatrends}
\end{adjustwidth}
\end{figure}
